{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-07 wacv_for_review.tex

\textbf{Deep Learning Features} Our focus so far was to build a high
speed tracker that can run about 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep Learning features, on
the other hand, recently have been proved to boost tracking accuracy
of some of the online tracking algorthms \cite{ma2015hierarchical,
  danelljan2015convolutional}. For this reason, we believe that, the
{\it E}nKCF tracker can perform better with deep learning features if
a target embedded system has GPUs.

@@

  I don't know why Figure 6 is presented separately from Figure 5. If
  you want to keep this way, you need, at least, to have their scales
  same -- precision should have the same range, say 0.8 as the max
  value.

  It seems most of reference on DNN hasn't added to the .bib file yet.
}

@@

Our {\it E}nKCF framework provides us flexibility to exploit different
feature  representations.  The  translation filters,  $R_{t}^{L}$  and
$R_{t}^{S}$,   considers  at   more  than   twice  larger   area  than
$R_{s}$.  Taking  this into  account,  we  can assign  deeper  feature
encodings  to $R_{s}$  as it  requires less  spatial information  than
$R_{t}^{L}$ and $R_{t}^{S}$.  Hence, we assign the  activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$  and $R_{t}^{S}$  are assigned the  activations of
the  second  layer  features  ($109\times109\times64$).  This  feature
assignment  is represented  as \textit{conv224-VGG}.  Additionally, we
assign  the  second convolutional  layer  features  to $R_{s}$  as  in
$R_{t}^{L}$    and    $R_{t}^{S}$    and    compare    this    setting
(\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the  VGGNet as
it provides  higher spatial resolution  at the first layers  than than
AlexNet \cite{krizhevsky2012imagenet}.

As shown in fig.~\ref{fig:UAV123_DATASET_DeepFeatures}, both settings
of the deep features outperform the HoG and color features as proposed
in {\it E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$
in success rates (AUC). On the other hand, the \textit{conv224-VGG}
setting performs slightly better than \textit{conv222-VGG} in
precision while achieving similar success rate (AUC).

\begin{figure}[h]
\begin{tabular}{ccc}
\tiny\quad\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

>>>>

\begin{table*}[h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table*}

\textbf{Evaluation with Deep Features}Our focus so far was to build a high
speed tracker that can run about 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep Learning features, on
the other hand, recently have been proved to boost tracking accuracy
of some of the online tracking algorthms \cite{ma2015hierarchical,
  danelljan2015convolutional}. For this reason, we believe that, the
{\it E}nKCF tracker can perform better with deep learning features if
a target embedded system has GPUs.

@@

  I don't know why Figure 7 is presented separately from Figure 5. If
  you want to keep this way, you need, at least, to have their scales
  same -- precision should have the same range, say 0.8 as the max
  value.
}

@@

Our {\it E}nKCF framework provides us flexibility to exploit different
level of abstractions in different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice larger area
than $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it requires less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first layers than than AlexNet
\cite{krizhevsky2012imagenet}.

As shown in fig.~\ref{fig:UAV123_DATASET_DeepFeatures}, both settings
of the deep features outperform the HoG and color features as proposed
in {\it E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$
in success rates (AUC). On the other hand, the \textit{conv224-VGG}
setting performs slightly better than \textit{conv222-VGG} in
precision while achieving similar success rate (AUC).  >>>>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target boundary information loss.}
\label{fig:Filters_CNN}
\end{figure}

\begin{figure}[t]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}
